---
title: "VAT Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}

library(flexdashboard)
library(ggplot2)
library(plotly)
library(data.table)
library(tidyr)
library(dplyr)
library(tidyverse)
library(knitr)
library(DT)
library(rpivotTable)
library(forecast)
library(openintro)
library(highcharter)
library(ggvis)
library(DataCombine)
library(viridisLite)
library(readxl)
library(reshape2)
options(warn=-1)
library(orca)

# R PLOTLY COLORS
# https://www.w3.org/TR/css-color-3/#svg-color 
# https://www.angularjswiki.com/fontawesome/finance/

  #rm(list = ls())

path<-"C:/Users/User/Documents/WB/VAT-GAP/3-New Version/VAT GAP in R/Model/DATA/INPUT"
setwd(path)
getwd()


# Import data business as usual
Results_1_bu <- read_excel("export_data_bu.xlsx",sheet="Results_1_bu")
revenue_vat_total_bu <- read_excel("export_data_bu.xlsx",sheet="revenue_vat_total_bu")
Est_Rev_bu<- read_excel("export_data_bu.xlsx",sheet="Est_Rev1_bu")
effective_vat_rates_bu<- read_excel("export_data_bu.xlsx",sheet="effective_vat_rates_bu")
hbs_bu<- read_excel("export_data_bu.xlsx",sheet="hbs_bu")
Simulation_Results_1_te<-read_excel("export_data_bu.xlsx",sheet="te_bu")

# Main result
Main_Results <- read_excel("export_data.xlsx",sheet="Main_Results")
Revenue_VAT_TOTAL <- read_excel("export_data.xlsx",sheet="Revenue_VAT_TOTAL")
Result_Simulation <- read_excel("export_data.xlsx",sheet="Result_Simulation")
Revenue_VAT_TOTAL <- read_excel("export_data.xlsx",sheet="Revenue_VAT_TOTAL")
Results_1 <- read_excel("export_data.xlsx",sheet="Results_1")
Est_Rev1<- read_excel("export_data.xlsx",sheet="Est_Rev1")
effective_vat_rates<-read_excel("export_data.xlsx",sheet="effective_vat_rates")
hbs<- read_excel("export_data.xlsx",sheet="hbs")

Simulation_Results_1<- read_excel("export_data.xlsx",sheet="Results_1")
Simulation<- read_excel("simulation.xlsx",sheet="simulation")
NACE_NAMES<- read_excel("simulation.xlsx",sheet="NACE_NAMES")





color_1 <- "#ba181b"



# Define fonts
t <- list(
        family = "Arial",
        size = 12
      )


t_8 <- list(
        family = "Arial",
        size = 8,
        face="bold"
      )

t_10 <- list(
        family = "Arial",
        size = 10,
        face="bold"
      )

        
```

# Intro

This dashboard include several types of results:

 - Decomposition of VAT GAP;
 - Simulation results from reform;
 - Structure of Non-refundable VAT;
 - Tax expenditures;
 - Effective VAT revenues;
 - Deciles groups household and
 - COICOP structure household.

Simulation parametars
=======================================================================


Row  {.tabset}
-----------------------------------------------------------------------

### Simulation parametars
```{r,eval=TRUE}

df<-Simulation%>%
  select(PRODUCT_INDUSTRY_CODE,Standard_VAT_Rate,Preferential_VAT_Rate,Simulated_Policy_Exempt,Simulated_Policy_Reduced_Rate,Simulated_Policy_Fully_Taxable)

df<-left_join(NACE_NAMES,df,by = c("PRODUCT_INDUSTRY_CODE"))%>%
dplyr::arrange(PRODUCT_INDUSTRY_CODE)


df<-df%>%
  dplyr::rename(c("NACE Division"= "PRODUCT_INDUSTRY_CODE",
                  "Description"= "PRODUCT_INDUSTRY_NAME",
                    "Standard Rate"="Standard_VAT_Rate",
                    "Preferential rate"="Preferential_VAT_Rate",
<<<<<<< HEAD
                    "Exempted Share"="Simulated_Policy_Exempt",
                  "Reduced Rate Share"= "Simulated_Policy_Reduced_Rate",
                  "Standard Rate Share"= "Simulated_Policy_Fully_Taxable"
=======
                    "Exempted Share(%)"="Simulated_Policy_Exempt",
                  "Reduced Rate Share (%)"= "Simulated_Policy_Reduced_Rate",
                  "Standard Rate Share (%)"= "Simulated_Policy_Fully_Taxable"
>>>>>>> c5c9091fedddd91e30e9a255d682739a267d618e
  ))




<<<<<<< HEAD
df$`Reduced Rate Share`<-round(df$`Reduced Rate Share`,4)
df$`Standard Rate Share`<-round(df$`Standard Rate Share`,4)
=======
df$`Reduced Rate Share (%)`<-round(df$`Reduced Rate Share (%)`,4)
df$`Standard Rate Share (%)`<-round(df$`Standard Rate Share (%)`,4)
>>>>>>> c5c9091fedddd91e30e9a255d682739a267d618e

datatable(df,
          caption = "Simulation parametars",
          rownames = T,
          filter = "top",
         extensions='Buttons',
          options = list(pageLength = 64,

          dom = 'Blfrtip',
          buttons=c('copy','csv','excel','print'),
          lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All"))))

```

### Notes

Decomposition of VAT GAP
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### **Comparison VAT Gap**
```{r,eval=TRUE}

df_plot<-Main_Results%>%
  dplyr::select(Total_VAT_Gap.M_of_denars,Policy_Gap.M_of_denars,Compliance_Gap.M_of_denars)%>%
  data.table()
colnames(df_plot) <- c('Total VAT Gap', 'Policy Gap ', 'Compliance Gap')

    df <-melt(df_plot) %>%
    dplyr:: arrange(desc(value))%>%
                  data.table()

    fig <- plot_ly(df, x = ~variable    , y = ~value, type = 'bar',
                    marker = list(color = c('#2ca02c', '#ff7f0e','#d62728')))
    fig <- fig%>% layout(title = " ", xaxis = list(title= ""),yaxis = list(title= " "),
                         annotations =
                           list(x = 0, y = -0.131,
                                title = "",
                                text = "",
                                showarrow = F,
                                xref='paper',
                                yref='paper',align='left')) #,font = t_8)

    fig
    

```


### **Total VAT Gap**
```{r,eval=TRUE}
df_plot<-Main_Results%>%
  dplyr::select(Total_VAT_Gap.Prc)%>%
  data.table()
colnames(df_plot) <- c('Total_VAT_Gap')

# gauge(round((df_plot$Total_VAT_Gap),
#           digits = 2),
#             min = 0,
#             max = 1,
#            gaugeSectors(success = c(0, 0.15),
#                          warning = c(0.15, 0.20),
#                          danger = c(0.3, 1),
#                          colors = c("green", "yellow", "red")))


gg.gauge <- function(pos,breaks=c(0,30,70,100)) {
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/100)
    th.end   <- pi*(1-b/100)
    th       <- seq(th.start,th.end,length=100)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="#2ca02c")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="#ff7f0e")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="#d62728")+
    geom_polygon(data=get.poly(pos-1,pos+1,0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5,vjust=0,
              aes(x=1.1*cos(pi*(1-breaks/100)),y=1.1*sin(pi*(1-breaks/100)),label=paste0(breaks,"%")))+
    annotate("text",x=0,y=0,label=pos,vjust=0,size=8)+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank()) 
}
gg.gauge(round(df_plot$Total_VAT_Gap*100,2),breaks=c(0,35,70,100))


```


### **Policy Gap**
```{r,eval=TRUE}
df_plot<-Main_Results%>%
  dplyr::select(Policy_Gap.Prc)%>%
  data.table()
colnames(df_plot) <- c('Policy Gap')

# gauge(round((df_plot$`Policy Gap`),
#           digits = 2),
#             min = 0,
#             max = 1,
#            gaugeSectors(success = c(0, 0.15),
#                          warning = c(0.15, 0.20),
#                          danger = c(0.3, 1),
#                          colors = c("green", "yellow", "red")))


gg.gauge <- function(pos,breaks=c(0,30,70,100)) {
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/100)
    th.end   <- pi*(1-b/100)
    th       <- seq(th.start,th.end,length=100)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="#2ca02c")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="#ff7f0e")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="#d62728")+
    geom_polygon(data=get.poly(pos-1,pos+1,0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5, vjust=0,
              aes(x=1.1*cos(pi*(1-breaks/100)),y=1.1*sin(pi*(1-breaks/100)),label=paste0(breaks,"%")))+
    annotate("text",x=0,y=0,label=pos,vjust=0,size=8)+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank()) 
}
gg.gauge(round(df_plot$`Policy Gap`*100,2),breaks=c(0,35,70,100))

```




Row
-----------------------------------------------------------------------

### **Comparison VAT revenues**

```{r,eval=TRUE}
 
 df_plot<-Main_Results%>%
  dplyr::select(Benchmark_VAT_M_of_denars,Uncalibrated_VAT_Est.M_of_denars,Calibrated_VAT_Est.M_of_denars)%>%
  data.table()
colnames(df_plot) <- c('Benchmark VAT', 'Uncalibrated VAT', 'Calibrated VAT')

    df <-melt(df_plot) %>%
    dplyr:: arrange(desc(value))%>%
                  data.table()

    fig <- plot_ly(df, x = ~variable    , y = ~value, type = 'bar',
                    marker = list(color = c('#2ca02c', '#ff7f0e','#d62728', '#1f77b4','#9370DB','#8c564b')))
    fig <- fig%>% layout(title = " ", xaxis = list(title= ""),yaxis = list(title= " "),
                         annotations =
                           list(x = 0, y = -0.131,
                                title = " ",
                                text = " ",
                                showarrow = F,
                                xref='paper',
                                yref='paper',align='left')) #,font = t_8)

    fig
                                  

```


### **Compliance GAP**

```{r,eval=TRUE}
df_plot<-Main_Results%>%
  dplyr::select(Compliance_Gap.Prc)%>%
  data.table()
colnames(df_plot) <- c('Compliance VAT Gap')

# gauge(round((df_plot$`Compliance VAT Gap`),
#             digits = 2),
#             min = 0,
#             max = 1,
#             gaugeSectors(success = c(0, 0.15),
#                          warning = c(0.15, 0.20),
#                          danger = c(0.3, 1),
#                          colors = c("green", "yellow", "red")))


gg.gauge <- function(pos,breaks=c(0,30,70,100)) {
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/100)
    th.end   <- pi*(1-b/100)
    th       <- seq(th.start,th.end,length=100)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="#2ca02c")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="#ff7f0e")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="#d62728")+
    geom_polygon(data=get.poly(pos-1,pos+1,0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5, vjust=0,
              aes(x=1.1*cos(pi*(1-breaks/100)),y=1.1*sin(pi*(1-breaks/100)),label=paste0(breaks,"%")))+
    annotate("text",x=0,y=0,label=pos,vjust=0,size=8)+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank()) 
}
gg.gauge(round(df_plot$`Compliance VAT Gap`*100,2),breaks=c(0,35,70,100))


```




### **C-Efficiency**

```{r,eval=TRUE}
VAT_COLLECTION2019<-52059
NOMINAL_GDP2019<- 550683

C_EFFICIENCY<-(VAT_COLLECTION2019/(NOMINAL_GDP2019*0.18))

# gauge(round((C_EFFICIENCY),
#             digits = 2),
#             min = 0,
#             max = 1,
#             gaugeSectors(success = c(0, 0.15),
#                          warning = c(0.15, 0.20),
#                          danger = c(0.3, 1),
#                          colors = c("green", "yellow", "red")))



gg.gauge <- function(pos,breaks=c(0,30,70,100)) {
  require(ggplot2)
  get.poly <- function(a,b,r1=0.5,r2=1.0) {
    th.start <- pi*(1-a/100)
    th.end   <- pi*(1-b/100)
    th       <- seq(th.start,th.end,length=100)
    x        <- c(r1*cos(th),rev(r2*cos(th)))
    y        <- c(r1*sin(th),rev(r2*sin(th)))
    return(data.frame(x,y))
  }
  ggplot()+ 
    geom_polygon(data=get.poly(breaks[1],breaks[2]),aes(x,y),fill="#2ca02c")+
    geom_polygon(data=get.poly(breaks[2],breaks[3]),aes(x,y),fill="#ff7f0e")+
    geom_polygon(data=get.poly(breaks[3],breaks[4]),aes(x,y),fill="#d62728")+
    geom_polygon(data=get.poly(pos-1,pos+1,0.2),aes(x,y))+
    geom_text(data=as.data.frame(breaks), size=5,  vjust=0,
              aes(x=1.1*cos(pi*(1-breaks/100)),y=1.1*sin(pi*(1-breaks/100)),label=paste0(breaks,"%")))+
    annotate("text",x=0,y=0,label=pos,vjust=0,size=8)+
    coord_fixed()+
    theme_bw()+
    theme(axis.text=element_blank(),
          axis.title=element_blank(),
          axis.ticks=element_blank(),
          panel.grid=element_blank(),
          panel.border=element_blank()) 
}
gg.gauge(round(C_EFFICIENCY*100,2),breaks=c(0,35,70,100))

```


Tax expenditures
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Total tax expenditures
```{r,eval=TRUE}

df_plot<-Simulation_Results_1_te #%>%
  #dplyr::select(Simulated_Change_in_Revenues.M_of_denars)


valueBox(round(sum(df_plot$Simulation_Results_1_te),0),
         icon="fa-chart-line",
          color = "blue")
```


### Tax expenditures accross NACE divisions

```{r,eval=TRUE}
 
dat_r<-Est_Rev_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()

dat_te<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()


 dat<-left_join(dat_r,dat_te,by = c("PRODUCT_INDUSTRY_CODE"))%>%
   #dplyr::mutate(te=Final_Demand_Total.y-Final_Demand_Total.x)%>%
   select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total.y,Final_Demand_Total.x)


#dat <-as.data.table(PLOT_PLOTLY)
colnames(dat) <- c('NACE', 'vat_revenue_before','vat_revenue_after')

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~vat_revenue_before, type = 'bar', name = 'With current VAT rates') %>% 
  add_trace(x = ~NACE, y = ~vat_revenue_after, type = 'bar', name = 'With standard VAT rates') %>% 
    layout(
       xaxis = list(title = '',font = t_8), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'#,#,font = t_8
     )


plt



```

Row
-----------------------------------------------------------------------

### Percentage change in VAT revenues
```{r,eval=TRUE}

# df_plot<-Simulation_Results_1%>%
#   dplyr::select(Simulated_Change_in_Revenues.Prc)
# df_plot$Simulation_Results_1_te
# Main_Results$Calibrated_VAT_Est.M_of_denars

valueBox(round((df_plot$Simulation_Results_1_te/Main_Results$Calibrated_VAT_Est.M_of_denars)*100,2),
         icon="fa-chart-pie",
          color = "red")
```


### Tax expenditures

```{r,eval=TRUE}

dat_r<-Est_Rev_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()

dat_te<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()


 dat<-left_join(dat_r,dat_te,by = c("PRODUCT_INDUSTRY_CODE"))%>%
   dplyr::mutate(te=Final_Demand_Total.y-Final_Demand_Total.x)%>%
   select(PRODUCT_INDUSTRY_CODE,te)


#dat <-as.data.table(PLOT_PLOTLY)
colnames(dat) <- c('NACE', 'te')

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~te, type = 'bar', name = 'Before reform') %>% 
    layout(
       xaxis = list(title = '',font = t_8), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'#,#,font = t_8
     )


plt


```


Simulation results
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Fiscal impact of simulation
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.M_of_denars)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.M_of_denars),0),
         icon="fa-chart-area",
          color = "blue")
```


### VAT revenues (before and after reform)

```{r,eval=TRUE}
 
dat_r<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()

dat_ba<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()


 dat<-left_join(dat_r,dat_ba,by = c("PRODUCT_INDUSTRY_CODE"))



colnames(dat) <- c('NACE', 'series1', 'series2')

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~series2, type = 'bar', name = 'Before reform') %>% 
  add_trace(x = ~NACE, y = ~series1, type = 'bar', name = 'After reform') %>% 
  layout(
       xaxis = list(title = '',font = t_8), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'
    #legend = list(orientation = 'h')
     )


plt



```

Row
-----------------------------------------------------------------------

### Percentage change in VAT revenues
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.Prc)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.Prc),2),
         icon="fa-chart-pie",
          color = "red")
```


### Difference of revenue after reform

```{r,eval=TRUE}

dat_r<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()

dat_ba<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Total)%>%
  data.table()


 dat<-left_join(dat_r,dat_ba,by = c("PRODUCT_INDUSTRY_CODE"))


colnames(dat) <- c('NACE', 'series1', 'series2')

dat$diff<-dat$series1-dat$series2

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~diff, type = 'bar', name = 'Before reform') %>% 
 # add_trace(x = ~NACE, y = ~series1, type = 'bar', name = 'After reform') %>% 
  layout(
       xaxis = list(title = '',font = t_8), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'#,#,font = t_8
    #legend = list(orientation = 'h')
     )


plt


```










Industries
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### VAT revenues from Industries 
```{r,eval=TRUE}

df_plot<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Total_Revenues_from_Intermediate_Inputs)


valueBox(round(sum(df_plot$Total_Revenues_from_Intermediate_Inputs),0),
         icon="fa-chart-pie",
          color = "blue")
```


### VAT revenues from industries (Before reform)

```{r,eval=TRUE}

df<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Total_Revenues_from_Intermediate_Inputs)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title="", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Intermediate Inputs", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)# )
    
    treemap

    



``` 

Row
-----------------------------------------------------------------------

### VAT revenues from industries
```{r,eval=TRUE}

df_plot<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Total_Revenues_from_Intermediate_Inputs)


valueBox(round(sum(df_plot$Total_Revenues_from_Intermediate_Inputs),0),
         icon="fa-chart-pie",
          color = "red")
```



###  VAT revenues from industries (After reform)

```{r,eval=TRUE}
 
df<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Total_Revenues_from_Intermediate_Inputs)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    
   df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title=" ", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Households", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)
    
    treemap
    


```





NPISH
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### VAT revenues from NPISH 
```{r,eval=TRUE}

df_plot<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_NPISH)


valueBox(round(sum(df_plot$Final_Demand_NPISH),0),
         icon="fa-chart-pie",
          color = "blue")
```


### VAT revenues from NPISH (Before reform)

```{r,eval=TRUE}

df<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_NPISH)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title="", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Intermediate Inputs", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)# )
    
    treemap

    



``` 

Row
-----------------------------------------------------------------------

### VAT revenues from NPISH
```{r,eval=TRUE}

df_plot<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_NPISH)


valueBox(round(sum(df_plot$Final_Demand_NPISH),0),
         icon="fa-chart-pie",
          color = "red")
```



###  VAT revenues from NPISH (After reform)

```{r,eval=TRUE}
 
df<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_NPISH)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    
   df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title=" ", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Households", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)
    
    treemap
    


```



Government
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### VAT revenues from Government 
```{r,eval=TRUE}

df_plot<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Government)


valueBox(round(sum(df_plot$Final_Demand_Government),0),
         icon="fa-chart-pie",
          color = "blue")
```


### VAT revenues from Government (Before reform)

```{r,eval=TRUE}

df<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Government)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title="", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Intermediate Inputs", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)# )
    
    treemap

    



``` 

Row
-----------------------------------------------------------------------

### VAT revenues from Government
```{r,eval=TRUE}

df_plot<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Government)


valueBox(round(sum(df_plot$Final_Demand_Government),0),
         icon="fa-chart-pie",
          color = "red")
```



###  VAT revenues from Government (After reform)

```{r,eval=TRUE}
 
df<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_Government)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    
   df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title=" ", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Households", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)
    
    treemap
    


```

Households
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### VAT revenues from households 
```{r,eval=TRUE}

df_plot<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_HH)


valueBox(round(sum(df_plot$Final_Demand_HH),0),
         icon="fa-chart-pie",
          color = "blue")
```


### VAT revenues from households (Before reform)

```{r,eval=TRUE}

df<-revenue_vat_total_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_HH)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title="", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Intermediate Inputs", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)# )
    
    treemap

    



``` 

Row
-----------------------------------------------------------------------

### VAT revenues from households
```{r,eval=TRUE}

df_plot<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_HH)


valueBox(round(sum(df_plot$Final_Demand_HH),0),
         icon="fa-chart-pie",
          color = "red")
```



###  VAT revenues from households (After reform)

```{r,eval=TRUE}
 
df<-Revenue_VAT_TOTAL%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,Final_Demand_HH)

    df<-melt(df)

    df<-df%>%
      dplyr::mutate(value=round(value),0)
    
    
   df$SUT_division<-"NACE Divisions"

    treemap<-plot_ly(data = df,
                                 type= "treemap",
                                 values= ~value,
                                 labels= ~PRODUCT_INDUSTRY_CODE,
                                 parents=  ~SUT_division,
                                 domain= list(column=0),
                                 name = " ",
                                 textinfo="label+value+percent parent")  %>%
                                 layout(title=" ", font = t,
                                 annotations =
                                 list(x = 0, y = -0.1,
                                 title = "VAT revenues from Households", 
                                 text = "Source: WB staff estimation",
                                 showarrow = F,
                                 xref='paper',
                                 yref='paper'),font = t)
    
    treemap
    


```

Effective VAT rates
=======================================================================

Row {data-height=850}
-----------------------------------------------------------------------

### Fiscal impact of simulation
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.M_of_denars)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.M_of_denars),0),
         icon="fa-chart-area",
          color = "blue")
```




### Effective VAT rates accross NACE division

```{r,eval=TRUE}

 dat_r<-effective_vat_rates%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL)%>%
  data.table()

dat_te<-effective_vat_rates_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL)%>%
  data.table()


 dat<-left_join(dat_r,dat_te,by = c("PRODUCT_INDUSTRY_CODE"))%>%
   select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL.y,EFFECTIVE_VAT_RATE_TOTAL.x)
  dat[is.na(dat)] <- 0

colnames(dat) <- c('NACE', 'efective_VAT_bu','efective_VAT_r')

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~efective_VAT_bu, type = 'bar', name = 'Before reform') %>% 
  add_trace(x = ~NACE, y = ~efective_VAT_r, type = 'bar', name = 'After reform') %>% 
    layout(
    #     xaxis = #list(title = '',font = t_8)
    #    tickfont = list(size = 5), 
    # yaxis = list(title = ''),
    # legend = list(x = 0.9, y = 0.99),
    # barmode = 'group'#,#,font = t_8
      xaxis = list(title = ''#,
               #  tickfont = list(size = 8) # <<<<<< HERE
                 ), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'
     )

# plt <- plt%>% layout(
#                      legend = list(font=list(size = 8),orientation = 'h'))


plt
    
```

Row
-----------------------------------------------------------------------


### Percentage change in VAT revenues
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.Prc)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.Prc),2),
         icon="fa-chart-pie",
          color = "red")
```



###  Effective VAT rates difference (before and after reform)


```{r,eval=TRUE}

dat_r<-effective_vat_rates%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL)%>%
  data.table()

dat_te<-effective_vat_rates_bu%>%
  dplyr::select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL)%>%
  data.table()


 dat<-left_join(dat_r,dat_te,by = c("PRODUCT_INDUSTRY_CODE"))%>%
   select(PRODUCT_INDUSTRY_CODE,EFFECTIVE_VAT_RATE_TOTAL.x,EFFECTIVE_VAT_RATE_TOTAL.y)
  dat[is.na(dat)] <- 0

  dat<-dat%>%
    dplyr::mutate(diff_effective_rate=EFFECTIVE_VAT_RATE_TOTAL.x-EFFECTIVE_VAT_RATE_TOTAL.y)%>%
    dplyr::select(PRODUCT_INDUSTRY_CODE,diff_effective_rate)
  
colnames(dat) <- c('NACE', 'diff_effective_rate')

plt <- plot_ly(dat) %>% 
  add_trace(x = ~NACE, y = ~diff_effective_rate, type = 'bar', name = 'Before reform') %>% 
  #add_trace(x = ~NACE, y = ~efective_VAT_r, type = 'bar', name = 'After reform') %>% 
    layout(
       xaxis = list(title = '',font = t_8), 
    yaxis = list(title = ''),
    legend = list(x = 0.9, y = 0.99),
    barmode = 'group'#,#,font = t_8
     )


plt
                    
```

COICOP 
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Fiscal impact of simulation
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.M_of_denars)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.M_of_denars),0),
         icon="fa-chart-area",
          color = "blue")
```


### VAT revenues from households by COICOP (Before reform)

```{r,eval=TRUE}

dat_r<-hbs_bu%>%
  #dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
  dplyr::select(deciles,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
                              "Alcoholic Beverages Tobacco and Narcotics",
                              "Clothing and footwear",
                              "Housing Water,Electricity,Gas and Other Fuels",
                              "Furnishings Household Equipment etc.",
                              "Health",
                              "Transport",
                              "Communication",
                              "Recreation and Culture",
                              "Education",
                              "Restaurants and Hotels",
                              "Miscellaneous Goods and Services")
                              

dat_r1<-dat_r%>%
  #dplyr::group_by(DECILE_THRESHOLD)%>%
  dplyr::group_by(deciles)%>%
  dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
                   `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
                   `Clothing and footwear` = sum(`Clothing and footwear`),
                   `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
                   `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
                   `Health` = sum(`Health`),
                   `Transport` = sum(`Transport`),
                   `Communication` = sum(`Communication`),
                   `Recreation and Culture` = sum(`Recreation and Culture`),
                   `Education` = sum(`Education`),
                   `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
                   `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))
                   
                   
    
#t_df1<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
t_df1<-melt(dat_r1, id.vars = c("deciles"))
t_df1$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
                                                 "chartreuse","orange","purple", "gold","tomato",
                                                 "darkturquoise", "forestgreen"))


    fig<-t_df1 %>% 
        plot_ly(labels = ~variable, values = ~value)
        fig <- fig %>% add_pie(hole = 0.6)
        fig <- fig %>% layout(
                  title = " ",  
                  showlegend = T,
                  xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  annotations =
                           list(x = 0, y = -0.1,
                                text = "Source: ",
                                showarrow = F,
                                xref='paper',
                                yref='paper'),font = t)
    # fig <- fig%>% layout(
    #                  legend = list(font=list(size = 8)))
                     
                     
            
        
    fig



```

Row
-----------------------------------------------------------------------

### Percentage change in VAT revenues
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.Prc)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.Prc),2),
         icon="fa-chart-pie",
          color = "red")
```


### VAT revenues from households by COICOP (After reform)

```{r,eval=TRUE}

dat_r<-hbs%>%
  #dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
  dplyr::select(deciles,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
                              "Alcoholic Beverages Tobacco and Narcotics",
                              "Clothing and footwear",
                              "Housing Water,Electricity,Gas and Other Fuels",
                              "Furnishings Household Equipment etc.",
                              "Health",
                              "Transport",
                              "Communication",
                              "Recreation and Culture",
                              "Education",
                              "Restaurants and Hotels",
                              "Miscellaneous Goods and Services")
                              

dat_r1<-dat_r%>%
  #dplyr::group_by(DECILE_THRESHOLD)%>%
  dplyr::group_by(deciles)%>%
  dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
                   `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
                   `Clothing and footwear` = sum(`Clothing and footwear`),
                   `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
                   `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
                   `Health` = sum(`Health`),
                   `Transport` = sum(`Transport`),
                   `Communication` = sum(`Communication`),
                   `Recreation and Culture` = sum(`Recreation and Culture`),
                   `Education` = sum(`Education`),
                   `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
                   `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))
                   
                   
    
#t_df1<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
t_df1<-melt(dat_r1, id.vars = c("deciles"))
t_df1$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
                                                 "chartreuse","orange","purple", "gold","tomato",
                                                 "darkturquoise", "forestgreen"))


    fig<-t_df1 %>% 
        plot_ly(labels = ~variable, values = ~value)
        fig <- fig %>% add_pie(hole = 0.6)
        fig <- fig %>% layout(
                  title = " ",  
                  showlegend = T,
                  xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
                  annotations =
                           list(x = 0, y = -0.1,
                                text = "Source: ",
                                showarrow = F,
                                xref='paper',
                                yref='paper'),font = t)

        
    fig
```



Decile groups 
=======================================================================

Row {data-height=650}
-----------------------------------------------------------------------

### Fiscal impact of simulation
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.M_of_denars)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.M_of_denars),0),
         icon="fa-chart-area",
          color = "blue")
```


### VAT revenues by decile groups (Before reform)

```{r,eval=TRUE}

# Original
dat_r<-hbs_bu%>%
  #dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
  dplyr::select(deciles,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
                              "Alcoholic Beverages Tobacco and Narcotics",
                              "Clothing and footwear",
                              "Housing Water,Electricity,Gas and Other Fuels",
                              "Furnishings Household Equipment etc.",
                              "Health",
                              "Transport",
                              "Communication",
                              "Recreation and Culture",
                              "Education",
                              "Restaurants and Hotels",
                              "Miscellaneous Goods and Services")


dat_r1<-dat_r%>%
  #dplyr::group_by(DECILE_THRESHOLD)%>%
  dplyr::group_by(deciles)%>%
  dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
                   `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
                   `Clothing and footwear` = sum(`Clothing and footwear`),
                   `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
                   `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
                   `Health` = sum(`Health`),
                   `Transport` = sum(`Transport`),
                   `Communication` = sum(`Communication`),
                   `Recreation and Culture` = sum(`Recreation and Culture`),
                   `Education` = sum(`Education`),
                   `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
                   `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))



#t_df1<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
t_df1<-melt(dat_r1, id.vars = c("deciles"))
t_df1$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
                                                 "chartreuse","orange","purple", "gold","tomato",
                                                 "darkturquoise", "forestgreen"))


#Expenditure_chart <- plot_ly(t_df1, x = ~DECILE_THRESHOLD, y = ~value,
Expenditure_chart <- plot_ly(t_df1, x = ~deciles, y = ~value,
                             type = 'bar',
                             marker = list(color = ~color), name = ~variable) %>%
                              layout(
                                xaxis = list(title = ''
                                ),
                                yaxis = list(title = ''),
                                legend = list(x = 0.01, y = 0.99,font = t_10),
                                tickfont = list(size = 5),
                                barmode = 'stack')

Expenditure_chart
# 
# 




```

Row
-----------------------------------------------------------------------

### Percentage change in VAT revenues
```{r,eval=TRUE}

df_plot<-Result_Simulation%>%
  dplyr::select(Simulated_Change_in_Revenues.Prc)


valueBox(round(sum(df_plot$Simulated_Change_in_Revenues.Prc),2),
         icon="fa-chart-pie",
          color = "red")
```


### VAT revenues by decile groups (After reform)

```{r,eval=TRUE}

# dat_r<-hbs%>%
#   dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
# colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
#                               "Alcoholic Beverages Tobacco and Narcotics",
#                               "Clothing and footwear",
#                               "Housing Water,Electricity,Gas and Other Fuels",
#                               "Furnishings Household Equipment etc.",
#                               "Health",
#                               "Transport",
#                               "Communication",
#                               "Recreation and Culture",
#                               "Education",
#                               "Restaurants and Hotels",
#                               "Miscellaneous Goods and Services")
# 
# 
# dat_r1<-dat_r%>%
#   dplyr::group_by(DECILE_THRESHOLD)%>%
#   dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
#                    `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
#                    `Clothing and footwear` = sum(`Clothing and footwear`),
#                    `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
#                    `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
#                    `Health` = sum(`Health`),
#                    `Transport` = sum(`Transport`),
#                    `Communication` = sum(`Communication`),
#                    `Recreation and Culture` = sum(`Recreation and Culture`),
#                    `Education` = sum(`Education`),
#                    `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
#                    `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))
# 
# 
# 
# t_df1<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
# t_df1$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
#                                                  "chartreuse","orange","purple", "gold","tomato",
#                                                  "darkturquoise", "forestgreen"))
# 
# 
# Expenditure_chart <- plot_ly(t_df1, x = ~DECILE_THRESHOLD, y = ~value,
#                              type = 'bar',
#                              marker = list(color = ~color), name = ~variable) %>%
#                               layout(
#                                 xaxis = list(title = ''
#                                 ),
#                                 yaxis = list(title = ''),
#                                 legend = list(x = 0.01, y = 0.99,font = t_10),
#                                 tickfont = list(size = 5),
#                                 barmode = 'stack')
# 
# 
# Expenditure_chart

# 
# 
dat_r<-hbs_bu%>%
  #dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
  dplyr::select(deciles,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
                              "Alcoholic Beverages Tobacco and Narcotics",
                              "Clothing and footwear",
                              "Housing Water,Electricity,Gas and Other Fuels",
                              "Furnishings Household Equipment etc.",
                              "Health",
                              "Transport",
                              "Communication",
                              "Recreation and Culture",
                              "Education",
                              "Restaurants and Hotels",
                              "Miscellaneous Goods and Services")


dat_r1<-dat_r%>%
  #dplyr::group_by(DECILE_THRESHOLD)%>%-
  dplyr::group_by(deciles)%>%
  dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
                   `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
                   `Clothing and footwear` = sum(`Clothing and footwear`),
                   `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
                   `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
                   `Health` = sum(`Health`),
                   `Transport` = sum(`Transport`),
                   `Communication` = sum(`Communication`),
                   `Recreation and Culture` = sum(`Recreation and Culture`),
                   `Education` = sum(`Education`),
                   `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
                   `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))



#t_df1<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
t_df1<-melt(dat_r1, id.vars = c("deciles"))
t_df1$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
                                                 "chartreuse","orange","purple", "gold","tomato",
                                                 "darkturquoise", "forestgreen"))


# Expenditure_chart <- plot_ly(t_df1, x = ~DECILE_THRESHOLD, y = ~value,
#                              type = 'bar',
#                              marker = list(color = ~color), name = ~variable) %>%
#   layout(
#     xaxis = list(title = ''
#     ),
#     yaxis = list(title = ''),
#     legend = list(x = 0.01, y = 0.99,font = t_10),
#     tickfont = list(size = 5),
#     barmode = 'stack')

#Expenditure_chart


dat_r<-hbs%>%
  #dplyr::select(DECILE_THRESHOLD,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
  dplyr::select(deciles,`01`,`02`,`03`,`04`,`05`,`06`,`07`,`08`,`09`,`10`,`11`,`12`)
colnames(dat_r)[c(2:13)] <- c("Food and Non-Alcoholic Beverages",
                              "Alcoholic Beverages Tobacco and Narcotics",
                              "Clothing and footwear",
                              "Housing Water,Electricity,Gas and Other Fuels",
                              "Furnishings Household Equipment etc.",
                              "Health",
                              "Transport",
                              "Communication",
                              "Recreation and Culture",
                              "Education",
                              "Restaurants and Hotels",
                              "Miscellaneous Goods and Services")


dat_r1<-dat_r%>%
  #dplyr::group_by(DECILE_THRESHOLD)%>%
  dplyr::group_by(deciles)%>%
  dplyr::summarise(`Food and Non-Alcoholic Beverages` = sum(`Food and Non-Alcoholic Beverages`),
                   `Alcoholic Beverages Tobacco and Narcotics` = sum(`Alcoholic Beverages Tobacco and Narcotics`),
                   `Clothing and footwear` = sum(`Clothing and footwear`),
                   `Housing Water,Electricity,Gas and Other Fuels` = sum(`Housing Water,Electricity,Gas and Other Fuels`),
                   `Furnishings Household Equipment etc.` = sum(`Furnishings Household Equipment etc.`),
                   `Health` = sum(`Health`),
                   `Transport` = sum(`Transport`),
                   `Communication` = sum(`Communication`),
                   `Recreation and Culture` = sum(`Recreation and Culture`),
                   `Education` = sum(`Education`),
                   `Restaurants and Hotels` = sum(`Restaurants and Hotels`),
                   `Miscellaneous Goods and Services` = sum(`Miscellaneous Goods and Services`))



#t_df2<-melt(dat_r1, id.vars = c("DECILE_THRESHOLD"))
t_df2<-melt(dat_r1, id.vars = c("deciles"))
t_df2$color <- factor(t_df1$variable, labels = c("royalblue", "cyan", "darkorange", "red", "brown",
                                                 "chartreuse","orange","purple", "gold","tomato",
                                                 "darkturquoise", "forestgreen"))

#
# Expenditure_chart <- plot_ly(t_df2, x = ~DECILE_THRESHOLD, y = ~value,
#                              type = 'bar',
#                              marker = list(color = ~color), name = ~variable) %>%
#   layout(
#     xaxis = list(title = ''
#     ),
#     yaxis = list(title = ''),
#     legend = list(x = 0.01, y = 0.99,font = t_10),
#     tickfont = list(size = 5),
#     barmode = 'stack')
#
#
# Expenditure_chart

#colnames(t_df3)
#

t_df3<-left_join(t_df1,t_df2,by = c("variable"))

t_df1<-t_df1%>%
  dplyr:: rename(c("variable.x"= "variable",
                   "value.x"="value",
                   "color.x"="color"

  ))



t_df3<-cbind(t_df1,t_df2)

#View(t_df3)
#colnames(t_df3)




plt <- plot_ly(t_df3) %>%
  add_trace(x = ~deciles, y = ~value.x, type = 'bar',name = 'Before reform',marker = list(color = ~color.x), name = ~variable.x) %>%
  add_trace(x = ~deciles, y = ~value, type = 'bar',name = 'After reform', marker = list(color = ~color), name = ~variable) %>%
  layout(
    xaxis = list(title = '',font = t_8),
    yaxis = list(title = ''),
    legend = list(x = 0.01, y = 0.99,font = t_10),
    barmode = 'bar'#,#,font = t_8
  )


plt


```

<<<<<<< HEAD
=======

>>>>>>> c5c9091fedddd91e30e9a255d682739a267d618e

